---
title: "Addressing Heteroscedasticity"
author: "Polina Prinii"
date: "12/10/2021"
output: html_document
---

This docuemnt is for the purpose of resolving heteroscedasticity showing in our regresssion analyis. -->

We start by plotting Histograms of all variables involved within the dataset.
This will determine which variables are showing skewness. 

Reading the csv file from git source.
```{r}
covid_data <- read.csv(url("https://raw.githubusercontent.com/polinaprinii/DAP-Project/main/Linear%20Regression%20Final%20Dataset/finaldataset.csv?token=ASV4RS53A5KFKKQPPSB66ADBXOW7C"))
```

Display first 6 rows of said csv file. 
```{r}
head(covid_data)

```

Setting varibales for all x and y variables within the dataset under analysis. 
```{r}

confirmed <- covid_data$Confirmed
deaths <- covid_data$Deaths
tests <- covid_data$tests
stringecy <- covid_data$MaxStringencyIndex
facialCov <- covid_data$MeanFacialCoverings
MaxstayHome <- covid_data$MaxStayHome
MeanstayHome <- covid_data$MeanStayHome
vaccines <- covid_data$totalvaccinations
boosters <- covid_data$totalbooster
people <- covid_data$fullyvacnumber

```
