---
title: "Addressing Heteroscedasticity"
author: "Polina Prinii"
date: "12/10/2021"
output: html_document
---

This docuemnt is for the purpose of resolving heteroscedasticity showing in our regression analyis. -->

```{r}
library(dplyr)
```

We start by plotting Histograms of all variables involved within the dataset.
This will determine which variables are showing skewness. 

Reading the csv file from git source.
```{r}
covid_data <- read.csv(url("https://raw.githubusercontent.com/polinaprinii/DAP-Project/main/Linear%20Regression%20Final%20Dataset/finaldataset.csv?token=ASV4RS53A5KFKKQPPSB66ADBXOW7C"))
```

Display first 6 rows of said csv file. 
```{r}
head(covid_data)

```

Setting varibales for all x and y variables within the dataset under analysis. 
```{r}

confirmed <- covid_data$Confirmed
deaths <- covid_data$Deaths
tests <- covid_data$tests
stringecy <- covid_data$MaxStringencyIndex
facialCov <- covid_data$MeanFacialCoverings
MaxstayHome <- covid_data$MaxStayHome
MeanstayHome <- covid_data$MeanStayHome
vaccines <- covid_data$totalvaccinations
boosters <- covid_data$totalbooster
people <- covid_data$fullyvacnumber

```

Plotting all histograms:

- Confirmed Cases Histo:
```{r}
hist(confirmed)
```
The above shows intense skewness to the right, a good candidate for log of nature function. 

- Deaths Cases Histo:
```{r}
hist(deaths)
```
The above shows intense skewness to the right, a good candidate for log of nature function.

- Tests  Histo:
```{r}
hist(tests)
```
The above shows intense skewness to the right, a good candidate for log of nature function.

- Stringency Histo:
```{r}
hist(stringecy)
```
The above shows slight skewness to the left, may not be a good candidate for log of nature function.

- Facial coverings Histo:
```{r}
hist(facialCov)
```
The above shows slight skewness to the left, may not be a good candidate for log of nature function.

- Max Stay Home Histo:
```{r}
hist(MaxstayHome)
```
Overall a good distribution between left and right.

- Mean Stay Home Histo:
```{r}
hist(MeanstayHome)
```
The above shows weak skewness to the left, may not be a good candidate for log of nature function.

- Vaccines Histo:
```{r}
hist(vaccines)
```
The above shows intense skewness to the right, a good candidate for log of nature function.

- Boosters Histo:
```{r}
hist(boosters)
```
The above shows intense skewness to the right, a good candidate for log of nature function.

- People fully vaccinated Histo:
```{r}
hist(people)
```
The above shows intense skewness to the right, a good candidate for log of nature function.

Out of the 10 variables, six will be transformed using the log of nature function and re-evaluated.
The 6 variables being (confirmed, deaths, tests, vaccines, boosters, people)

Transforming the columns, additionally we plot the Histo of the log() function immediately:

- Confirmed Cases Log & Histo:
```{r}
covid_data$logofConfirmed = log(covid_data$Confirmed)
hist(covid_data$logofConfirmed)

```
A bit of a better distribution with a slight skew to the left which could be interpreted as outliers. 

- Deaths Cases Log & Histo:
```{r}
covid_data$logofDeaths = log(covid_data$Deaths)
hist(covid_data$logofDeaths)

```

A somewhat perfect distribution. 

- Tests Cases Log & Histo:
```{r}
covid_data$logofTests = log(covid_data$tests)
hist(covid_data$logofTests)

```
An improvement in the distribution. 

- Vaccines  Log & Histo:
```{r}
covid_data$logofTotalVaccines = log(covid_data$totalvaccinations)
hist(covid_data$logofTotalVaccines)

```
An improvement in the distribution. 

- Boosters Log & Histo:
```{r}
covid_data$logofTotalBoosters = log(covid_data$totalbooster)
hist(covid_data$logofTotalBoosters)
```
An improvement in the distribution.

- People  Log & Histo:
```{r}
covid_data$logofFullyVaccinated = log(covid_data$fullyvacnumber)
hist(covid_data$logofFullyVaccinated)
head(covid_data)
write.csv(covid_data,"C:/Users/Rober/Documents/R/test.csv", row.names=TRUE)
```
An improvement in the distribution.

First we replace all instances of 'NA', 'Nan' and 'Inf' as the lm function can't read them, we will replace them with 0 using excel.
```{r}
write.csv(covid_data,"D:/Git/DAP-Project/Main Project - Covid-19 - Group Analysis/Data/Transformation.csv", row.names=TRUE)
```
1. Maria to address the correct procedure to changing 'NA', 'Nan' and 'Inf' instances to 0 via R and not excel.

```{r}
covid_data

```

Read csv file 
```{r}
coviddata2 <- read.csv("D:/Git/DAP-Project/Main Project - Covid-19 - Group Analysis/Data/Transformation.csv", header=TRUE)
coviddata2 <- coviddata2 %>%
  drop_na(logofConfirmed,logofDeaths,logofTests,logofTotalVaccines,logofTotalBoosters,logofFullyVaccinated)
coviddata2 <- coviddata2 %>%
  filter_all(all_vars(!is.infinite(.)))

coviddata2
```

```{r}
attach(coviddata2)
regressionmodel <- lm(logofDeaths ~ logofConfirmed + logofTests + MaxStringencyIndex + MeanStringencyIndex + MaxFacialCoverings + MeanFacialCoverings + MaxStayHome + MeanStayHome + logofTotalVaccines + logofFullyVaccinated+ logofTotalBoosters)
```
```{r}
lm_model2 <- coviddata2 %>%
  add_predictions(regressionmodel)%>%
  add_residuals(regressionmodel)

head(lm_model2)


```

```{r}
#Predicted deaths using linear model
ggplot(lm_model2)+
  geom_line(aes(MaxStringencyIndex, pred), col = "red")+
  geom_line(aes(MaxStringencyIndex,Deaths ))

```
```{r}
#plot residuals
ggplot(lm_model2,aes(MaxStringencyIndex, resid))+
  geom_ref_line(h=0)+
  geom_line()+
  labs(title="Residuals of the linear model")

```

```{r}
plot(regressionmodel)
```

```{r}
write.csv(coviddata2,"transformeddata.csv")

```

EVALUATION OF THE LINEAR REGRESSION MODEL 

```{r}
broom::glance(regressionmodel)
MAPE(lm_model2$pred,lm_model2$Deaths)
RMSE(lm_model2$pred,lm_model2$Deaths)
MAE(lm_model2$pred,lm_model2$Deaths)

```
R-squared is a goodness-of-fit measure for linear regression models. R-squared measures the strength of the relationship between our model and the dependent variables on a convenient 0 – 100% scale. In our case it is 95%, which is very good. There is an improvement from yesterday by 8% by addressing heteroscedasticity.  The p-value is tiny which indicates that we can reject the null hypothesis stating thet the coefficient is equal to 0 (have no effect).

The MAPE values is defined as actual to observed value minus the forecasted value. Value of 0.99 means
that our model’s predictions are, on average 1% off from the actual values.

Root Mean Square Error(RMSE) is the square root of MSE, which is a square root of the sum of square of predicted error (which is a real ouput minus predicted output and then divided by the number of data points). It gives us an absolute value on how much our predicted results deviate from the actual number.In our case it is 112 564.

The MAE value means that on average the forecasted distance from the true value is 50 403, which is OK as our values range from 35 to 615 636.

