---
title: "Covid 19"
author: "Maria Migrova"
date: "12/9/2021"
output:
  word_document: default
  html_document: default
---
```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(modelr)
library(Metrics)
library(MLmetrics)
library(lmtest)
library(robust)

```

```{r}
covid_data <- read.csv(url("https://raw.githubusercontent.com/polinaprinii/DAP-Project/main/Linear%20Regression%20Final%20Dataset/finaldataset.csv?token=ASV4RS53A5KFKKQPPSB66ADBXOW7C"))
```

```{r}
head(covid_data)

```

```{r}
lm_model <- lm(Deaths ~ Confirmed + tests + MaxStringencyIndex + MeanStringencyIndex + MaxFacialCoverings + MeanFacialCoverings + MaxStayHome + MeanStayHome + totalvaccinations + totalbooster + fullyvacnumber, data = covid_data)

```

```{r}
broom::glance(lm_model)

```

```{r}
lm_model1 <- covid_data %>%
  add_predictions(lm_model)%>%
  add_residuals(lm_model)

head(lm_model1)

```

```{r}
#Predicted Deaths using linear model
ggplot(lm_model1)+
  geom_line(aes(MaxStringencyIndex, pred), col = "red")+
  geom_line(aes(MaxStringencyIndex,Deaths ))
```


```{r}
#plot residuals
ggplot(lm_model1,aes(MaxStringencyIndex, resid))+
  geom_ref_line(h=0)+
  geom_line()+
  labs(title="Residuals of the linear model")

```
```{r}
plot(lm_model)

```

ASSUMPTIONS:

1. Residuals vs Fitted - this graph is showing heteroscedasticity.To correct this data. (POLINA TO CONTINUE THE VIOLATION)

2. At the second graph (Normal Q-Q) we can check the normality assumption. Our points follow a straight
line with some outliers around. This assumption is justified.The outliers are on line 36,110 and 77.

3. At the third graph (Scale – Location) we can check the constant variance assumption. We can notice heteroskedasticity in our model as the points are not located around a horizontal line but they follow a 'V' shape.

4. THe third graph shows us our outliers. The outliers are on line 24,36,77 (ALUN TO CONTINUE ON OUTLIERS)

```{r}
bptest(lm_model)

```


